---
title: "Glutamate Variability Meta-analysis"
output: html_notebook
---

# Packages
```{r}


install.packages("lmerTest")
install.packages("gridExtra")
install.packages("ggpubr")
install.packages("metafor")
install.packages("flextable")
install.packages("weights")
install.packages("tidyverse")
install.packages("readr")



library("metafor")
library("lmerTest")
library("tidyverse")
library("gridExtra")
library("ggpubr")
library("flextable")
library("weights")
library("readr")


```

# Clean Data
```{r}
# make sure you download the folder containing r scripts for 'data_clean' etc and put path below
sapply(list.files(pattern="[.]R$", path="C:/Users/Me/Analysis/R/variance/from_rob2/r_functions/r_functions/R_packages/", full.names=TRUE), source);

# load data
dat <- read_csv("C:/Users/Me/Analysis/R/variance/Github_Glu_Meta_analysis.csv")


# Calculate Hedges' G
dat <- escalc(measure="SMD", m1i=m1i, sd1i=sd1i, n1i=n1i, m2i=m2i, sd2i=sd2i, n2i=n2i_con, data = dat)
# this adds yi and vi to dataframe =  function "escalc" from the package metafor calculates effect size (yi), variance (vi)

# Correct the class of variables
dat$age_con <- as.numeric(dat$age_con)
dat$age_combined <- as.numeric(dat$age_combined)
dat$age_pt <- as.numeric(dat$age_pt)
dat$age_pt_sd <- as.numeric(dat$age_pt_sd)


dat$male_con <- as.numeric(dat$male_con)
dat$male_pt <- as.numeric(dat$male_pt)
dat$male_combined <- as.numeric(dat$male_combined)


```


```{r}

unique(dat$studyid) # how many original studies

```

```{r} 
# correlation between mean and sd - justifies using CVR instead of VR

dat$weightmean <- stdz(dat$m1i, weight=dat$n1i)
dat$weightsd  <- stdz(dat$sd1i, weight=dat$n1i)

ggplot(dat) +
  geom_point(aes(x = m1i, y=sd1i, colour = study, alpha = 0.05))

ggplot(dat) +
  geom_point(aes(x = weightmean, y=weightsd, colour = study, alpha = 0.05))

png('C:/Users/Me/Analysis/R/variance/results/correlations/sd_mean_corr2.png')

ggplot(data=dat , mapping = aes(x = m1i, y=sd1i, colour = study, alpha = 0.05, size = n1i)) +
  geom_point() +
  geom_smooth(aes(), method = lm,  size=0.5) +
  labs(
    x = "Mean Glutamatergic Metabolite Level",
    y = "SD of Glutamatergic Metabolite"
  ) +
  theme_minimal() +
  theme(legend.position = "none")

dev.off()

cor.test(dat$weightmean, dat$weightsd, 
                    method = "pearson") # (weighted r=0.69, p<0.001).


```








# Run all meta analyses
```{r}
#SMD  - to view, type meta_results
rm(meta_results) # this just removes previous meta-results you may have made
meta_results=c()
for (selected_region in unique(dat$region)){
  for (selected_metabolite in unique(dat$metabolite)){
      filtered_dat <- dat %>% filter(region==selected_region) %>% filter(metabolite==selected_metabolite)
      # Only run for studies k>2
      if(nrow(filtered_dat)>2){
        result <- rma(yi, vi, data=filtered_dat, method="REML", slab=paste(author, year, sep=", "), control=list(maxiter=1000, stepadj=0.5)) #, mods=naive1
        meta_results[[paste(selected_region, selected_metabolite, sep='_')]] <- result}}}

# VR
vr_meta <- function(selected_region, selected_metabolite, dat){
  dat_group_region <- dat %>% filter(region == selected_region, metabolite==selected_metabolite)
  if(nrow(dat_group_region)>2){
    vr_region_group <- Calc.lVR(dat_group_region$sd2i,  dat_group_region$n2i_con, dat_group_region$sd1i, dat_group_region$n1i)
    var_vr_region_group = Calc.var.lVR(dat_group_region$n2i_con, dat_group_region$n1i)
    region_group_vr_meta = rma.uni(yi=vr_region_group,vi=var_vr_region_group,method='REML', slab = paste(dat_group_region$author, dat_group_region$year, sep = " "), control=list(maxiter=1000, stepadj=0.5))
    return(region_group_vr_meta)}}

rm(vr_results)
vr_results=c()
for (selected_region in unique(dat$region)){
  for (selected_metabolite in unique(dat$metabolite)){
        vr_result <- vr_meta(selected_region, selected_metabolite, dat)
        vr_results[[paste(selected_region, selected_metabolite, sep='_')]] <- vr_result}}

# CVR
cvr_meta <- function(selected_region, selected_metabolite, dat){
  dat_group_region <- dat %>% filter(region == selected_region, metabolite==selected_metabolite)
  if(nrow(dat_group_region)>2){
    cvr_region_group <- Calc.lnCVR(dat_group_region$m2i, dat_group_region$sd2i,  dat_group_region$n2i_con, dat_group_region$m1i, dat_group_region$sd1i, dat_group_region$n1i)
  var_cvr_region_group = Calc.var.lnCVR(dat_group_region$m2i, dat_group_region$sd2i, dat_group_region$n2i_con, dat_group_region$m1i, dat_group_region$sd1i, dat_group_region$n1i)
  region_group_cvr_meta = rma.uni(yi=cvr_region_group,vi=var_cvr_region_group, verbose=TRUE,digits=5,control=list(maxiter=200), method='REML', slab = paste(dat_group_region$author, dat_group_region$year, sep = " "))
    return(region_group_cvr_meta)}}

rm(cvr_results)
cvr_results=c()
for (selected_region in unique(dat$region)){
  for (selected_metabolite in unique(dat$metabolite)){
        cvr_result <- cvr_meta(selected_region, selected_metabolite, dat)
        cvr_results[[paste(selected_region, selected_metabolite, sep='_')]] <- cvr_result}}


# to view, type vr_results
# vr_results
# cvr_results
# meta_results


```

# Functon to make the forest plots
```{r}
create_summary_plot<- function(meta_results, title){
  
  # Get region and metabolite labels
  to_include <- names(meta_results)
  label2 <- as.factor(str_sub(to_include,1,-5))
  label1 <- as.factor(str_sub(to_include,-3,-1))
  
  # Create Data Frame
  len = numeric(length(to_include))
  graph_results <- data.frame(estimate=len, lb=len, ub=len, k=len, p=len)
  graph_results$label1 <- label1
  graph_results$label2 <- label2
  #this bit is so that the numbers table and the forest plot have things in the same order
  graph_results$label1 <- factor(graph_results$label1, levels = unique(graph_results$label1)) 
  graph_results$label2 <- factor(graph_results$label2, levels = unique(graph_results$label2))
  
  # fill data frame with meta results
  j=1
  for (indiv_meta in to_include){
    graph_results$estimate[j]=meta_results[[indiv_meta]]$b
    graph_results$lb[j]=meta_results[[indiv_meta]]$ci.lb
    graph_results$ub[j]=meta_results[[indiv_meta]]$ci.ub
    graph_results$p[j]=meta_results[[indiv_meta]]$pval
    j=j+1
  }
  
  # Make forest plot
  p <- ggplot(data=graph_results) +
          geom_pointrange( aes(x=label1, y=estimate,  ymin=lb, ymax=ub), position = position_dodge(width = 0.9)) + 
          facet_grid(cols = vars(label2), scales = "free", space='free', switch = "x") +
          geom_hline(yintercept=0, lty=2) +  # add a dotted line at x=1 after flip
          ylab("") +
          xlab("")+
          scale_y_continuous(position="right")+
          theme_minimal() + # use a white background
          theme(legend.position="none")+
          theme(panel.background = element_rect(fill = NA, color = "grey"))+
          theme(strip.text.x=element_text(angle =180, hjust = 0.5))+
          theme(axis.text.x=element_text(angle = 90, hjust = 0.5))+
          theme(axis.text.y = element_text(angle = 90, hjust=0.5))+
          theme(strip.placement = 'outside')+
          scale_color_grey()
          
  # get data for table
  estimate = sprintf("%0.2f",round(graph_results$estimate, digits=3))
  pval = sprintf("%0.2f",round(graph_results$p, digits=4))
  k = graph_results$k
  
  # get confidence intervals
  cis = c()
  lbs <-  sprintf("%0.2f",round(graph_results$lb, digits=3))
  ubs <-  sprintf("%0.2f",round(graph_results$ub, digits=3))
  for(i in 1:length(lbs)){
    ci <- paste0("[",lbs[i],", ", ubs[i],"]")
    cis <- append(cis,ci)}
  
  seq(1)
  lab <- data.frame(V0 = rep(seq(1,by=0.6,length.out=length(graph_results$label1)),times=3),
                    #use V0 to adjust spacing between rows and V05 to adjust spacing between colums
                    V05 = rep(c(1.5,2,3),each=length(graph_results$label1)),
                    V1 = c(estimate,cis, pval))
  lab$V1 <- as.character(lab$V1)
  
  data_table <- ggplot(lab) +
      geom_text(aes(x = V0, y = V05, label = format(V1, nsmall = 1)),size = 3, hjust=0, vjust=0.0, angle=90) + theme_bw() +
      theme(panel.grid.major = element_blank(),
            panel.grid.minor = element_blank(),
            legend.position = "none",
            panel.border = element_blank(), 
            axis.text.x = element_text(colour="white"),#element_blank(), #can add a color here if you wannt to see cordinates to aid with positioning
            axis.text.y = element_text(colour="white"), 
            axis.ticks = element_line(colour="white"),#element_blank(),
            plot.margin = unit(c(0,0,0,0), "lines")) +
            labs(x="",y="") +
            coord_cartesian(xlim=c(0,13))+
            coord_cartesian(ylim=c(1,3.5))+
            xlim(0,12)
  
  return(list(data_table, annotate_figure(p, left=text_grob(title,  size = 8, rot=90), fig.lab.pos = 'top.right')))
}
```

# Draw the forest plots
```{r fig.height=8, fig.width=8}
# make sure folders exist
png('C:/Users/Me/Analysis/R/variance/results/smd/summary.png', width = 185, height = 120, units='mm', res = 400)
summary_smd <- create_summary_plot(meta_results, "SMD (95% CI)")
p <- grid.arrange(summary_smd[[1]], summary_smd[[2]], nrow=2)
dev.off()

png('C:/Users/Me/Analysis/R/variance/results/cvr/summary.png', width = 185, height = 120, units='mm', res = 400)
summary_cvr <- create_summary_plot(cvr_results, "CVR (95% CI)")
grid.arrange(summary_cvr[[1]], summary_cvr[[2]], nrow=2)
dev.off()

png('C:/Users/Me/Analysis/R/variance/results/vr/summary.png', width = 185, height = 120, units='mm', res = 400)
summary_vr <- create_summary_plot(vr_results, "VR (95% CI)")
grid.arrange(summary_vr[[1]], summary_vr[[2]], nrow=2)
dev.off()

```










# Year of publication, cpz, sex and age meta regression
```{r}
male_results = c()
age_results = c()
age_results_pt_sd = c()


panss_results_cvr = c()
panss_results_cvr_sd = c()
cpz_results_cvr = c()
male_results_cvr = c()
age_results_cvr = c()
age_results_cvr_pt_sd = c()


fwhm_ratio_results_cvr = c()
snr_ratio_results_cvr = c()

year_results_vr = c()
year_results_cvr = c()



for (reg in unique(dat$region)){
  for (metab in c('glu', 'gln', 'glx')){
    sub_dat <- dat %>% filter(region==reg & metabolite==metab)
    if(nrow(sub_dat)>2){
      age_met<- rma(yi, vi, data=sub_dat, method="REML", mods=age_combined,control=list(maxiter=1000, stepadj=0.5))
      age_met_pt_sd<- rma(yi, vi, data=sub_dat, method="REML", mods=age_pt_sd,control=list(maxiter=1000, stepadj=0.5))

      if (sum((sub_dat$male_combined>0), na.rm=TRUE)>2){male_met<- rma(yi, vi, data=sub_dat, method="REML", mods=male_combined,control=list(maxiter=1000, stepadj=0.5))}
      study_label = paste0(reg,'_', metab)
      male_results <- append(male_results,study_label)
      male_results <- append(male_results,c(male_met$b[[2]], male_met$se[2],male_met$pval[[2]]))
      age_results <- append(age_results,study_label)
      age_results <- append(age_results,c(age_met$b[[2]], age_met$se[2],age_met$pval[[2]]))
      age_results_pt_sd <- append(age_results_pt_sd,study_label)
      age_results_pt_sd <- append(age_results_pt_sd,c(age_met_pt_sd$b[[2]], age_met_pt_sd$se[2],age_met_pt_sd$pval[[2]]))
    
      cvr_region_group <- Calc.lnCVR(sub_dat$m2i, sub_dat$sd2i,  sub_dat$n2i_con, sub_dat$m1i, sub_dat$sd1i, sub_dat$n1i)
      var_cvr_region_group = Calc.var.lnCVR(sub_dat$m2i, sub_dat$sd2i, sub_dat$n2i_con, sub_dat$m1i, sub_dat$sd1i, sub_dat$n1i)
      region_group_cvr_meta = rma.uni(data=sub_dat,yi=cvr_region_group,vi=var_cvr_region_group,method='REML', slab = paste(sub_dat$author, sub_dat$year, sep = " "), mods=year,control=list(maxiter=1000, stepadj=0.5))
      year_results_cvr <- append(year_results_cvr, c(study_label, region_group_cvr_meta$b[[2]], region_group_cvr_meta$se[2], region_group_cvr_meta$pval[[2]]))
      
      region_group_cvr_meta = rma.uni(data=sub_dat,yi=cvr_region_group,vi=var_cvr_region_group,method='REML', slab = paste(sub_dat$author, sub_dat$year, sep = " "), mods=age_combined,control=list(maxiter=1000, stepadj=0.5))
      age_results_cvr <- append(age_results_cvr, c(study_label, region_group_cvr_meta$b[[2]], region_group_cvr_meta$se[2], region_group_cvr_meta$pval[[2]]))
      
      region_group_cvr_meta = rma.uni(data=sub_dat,yi=cvr_region_group,vi=var_cvr_region_group,method='REML', slab = paste(sub_dat$author, sub_dat$year, sep = " "), mods=age_pt_sd,control=list(maxiter=1000, stepadj=0.5))
      age_results_cvr_pt_sd <- append(age_results_cvr_pt_sd, c(study_label, region_group_cvr_meta$b[[2]], region_group_cvr_meta$se[2], region_group_cvr_meta$pval[[2]]))
      
      
# panss
      
      if (sum((sub_dat$panss_tot>0), na.rm=TRUE)>3){
      region_group_cvr_meta = rma.uni(data=sub_dat,yi=cvr_region_group,vi=var_cvr_region_group,method='REML', slab = paste(sub_dat$author, sub_dat$year, sep = " "), mods=panss_tot,control=list(maxiter=1000, stepadj=0.5))
      panss_results_cvr <- append(panss_results_cvr, c(study_label, region_group_cvr_meta$b[[2]], region_group_cvr_meta$se[2], region_group_cvr_meta$pval[[2]]))}
      
 
# panss sd           
            if (sum((sub_dat$panss_tot_sd>0), na.rm=TRUE)>3){
      region_group_cvr_meta = rma.uni(data=sub_dat,yi=cvr_region_group,vi=var_cvr_region_group,method='REML', slab = paste(sub_dat$author, sub_dat$year, sep = " "), mods=panss_tot_sd,control=list(maxiter=1000, stepadj=0.5))
      panss_results_cvr_sd <- append(panss_results_cvr_sd, c(study_label, region_group_cvr_meta$b[[2]], region_group_cvr_meta$se[2], region_group_cvr_meta$pval[[2]]))}
  
# cpz
      if (sum((sub_dat$cpz>0), na.rm=TRUE)>3){
      region_group_cvr_meta = rma.uni(data=sub_dat,yi=cvr_region_group,vi=var_cvr_region_group,method='REML', slab = paste(sub_dat$author, sub_dat$year, sep = " "), mods=cpz,control=list(maxiter=1000, stepadj=0.5))
      cpz_results_cvr <- append(cpz_results_cvr, c(study_label, region_group_cvr_meta$b[[2]], region_group_cvr_meta$se[2], region_group_cvr_meta$pval[[2]]))}
      
# male 
      if (sum((sub_dat$male_combined>0), na.rm=TRUE)>3){
      region_group_cvr_meta = rma.uni(data=sub_dat,yi=cvr_region_group,vi=var_cvr_region_group,method='REML', slab = paste(sub_dat$author, sub_dat$year, sep = " "), mods=male_combined,control=list(maxiter=1000, stepadj=0.5))
      male_results_cvr <- append(male_results_cvr, c(study_label, region_group_cvr_meta$b[[2]], region_group_cvr_meta$se[2], region_group_cvr_meta$pval[[2]]))}
      
#fwhm_ratio
        if (sum((sub_dat$fwhm_ratio>0), na.rm=TRUE)>3){
      region_group_cvr_meta = rma.uni(data=sub_dat,yi=cvr_region_group,vi=var_cvr_region_group,method='REML', slab = paste(sub_dat$author, sub_dat$year, sep = " "), mods=fwhm_ratio,control=list(maxiter=1000, stepadj=0.5))
      fwhm_ratio_results_cvr <- append(fwhm_ratio_results_cvr, c(study_label, region_group_cvr_meta$b[[2]], region_group_cvr_meta$se[2], region_group_cvr_meta$pval[[2]]))}
      
# snr
        if (sum((sub_dat$snr_ratio>0), na.rm=TRUE)>3){
      region_group_cvr_meta = rma.uni(data=sub_dat,yi=cvr_region_group,vi=var_cvr_region_group,method='REML', slab = paste(sub_dat$author, sub_dat$year, sep = " "), mods=snr_ratio,control=list(maxiter=1000, stepadj=0.5))
      snr_ratio_results_cvr <- append(snr_ratio_results_cvr, c(study_label, region_group_cvr_meta$b[[2]], region_group_cvr_meta$se[2], region_group_cvr_meta$pval[[2]]))}
      

vr_region_group <- Calc.lVR( sub_dat$sd2i,  sub_dat$n2i_con, sub_dat$sd1i, sub_dat$n1i)
      var_cvr_region_group = Calc.var.lVR( sub_dat$n2i_con,  sub_dat$n1i)
      region_group_vr_meta = rma.uni(data=sub_dat,yi=cvr_region_group,vi=var_cvr_region_group,method='REML', slab  = paste(sub_dat$author, sub_dat$year, sep = " "), mods=year,control=list(maxiter=1000, stepadj=0.5))
      year_results_vr <- append(year_results_vr,study_label)
     year_results_vr <- append(year_results_vr,region_group_vr_meta$pval[[2]])
    }
 }
 }

# View results by uncommenting below
# p value is last column
# estimate, 2 standard error, 3 p val


# male_results_cvr 
# age_results_cvr 
# age_results_pt_sd  

# panss_results_cvr
# panss_results_cvr_sd


# fwhm_ratio_results_cvr 
# snr_ratio_results_cvr 


# age cvr result 
# age_results_cvr_pt_sd


# cpz_results_cvr 


# metaregression of smd results:
# write.table(age_results)
# write.table(male_results)

# age_results
# male_results


```

```{r}
# meta-regression for panss smd 

panss_results = c()

for (reg in unique(dat$region)){
  for (metab in c('glu', 'gln', 'glx')){
    sub_dat <- dat %>% filter(region==reg & metabolite==metab)
    if(nrow(sub_dat)>2){
      
      if (sum((sub_dat$panss_tot>0), na.rm=TRUE)>3){
        panss_met<- rma(yi, vi, data=sub_dat, method="REML", mods=panss_tot,control=list(maxiter=1000, stepadj=0.5))
      study_label = paste0(reg,'_', metab)
      panss_results <- append(panss_results,study_label)
      panss_results <- append(panss_results,c(panss_met$b[[2]], panss_met$se[2],panss_met$pval[[2]]))}
    }
  }
}
      
# results
panss_results

```

```{r}
# meta-regression for cpz smd 

cpz_results = c()

for (reg in unique(dat$region)){
  for (metab in c('glu', 'gln', 'glx')){
    sub_dat <- dat %>% filter(region==reg & metabolite==metab)
#    sub_dat <- sub_dat %>% filter(cpz>0)
    if(nrow(sub_dat)>2){
      
      if (sum((sub_dat$cpz>0), na.rm=TRUE)>2){
        cpz_met<- rma(yi, vi, data=sub_dat, method="REML", mods=cpz,control=list(maxiter=1000, stepadj=0.5))
      study_label = paste0(reg,'_', metab)
      cpz_results <- append(cpz_results,study_label)
      cpz_results <- append(cpz_results,c(cpz_met$b[[2]], cpz_met$se[2],cpz_met$pval[[2]]))}
    }
  }
}
      
      # metaregression of smd results:?
# write.table(cpz_results)
cpz_results

```

















# MODERATE BY MEDICATION
```{r}
# MODERATE BY MED 
# bg glx
dat_bg_glx_cvr <- filter(dat, region == "bg", metabolite == "glx" )

# calc cvr
    dat_bg_glx_cvr2 <- Calc.lnCVR(dat_bg_glx_cvr$m2i, dat_bg_glx_cvr$sd2i,  dat_bg_glx_cvr$n2i_con, dat_bg_glx_cvr$m1i, dat_bg_glx_cvr$sd1i, dat_bg_glx_cvr$n1i)
# does this add yi to dataframe or 'cvr', if cvr, then should this fo on rma below?    
dat_bg_glx_cvr$cvr <- dat_bg_glx_cvr2

# calc cvr var    
  dat_bg_glx_VARcvr <- Calc.var.lnCVR(dat_bg_glx_cvr$m2i, dat_bg_glx_cvr$sd2i, dat_bg_glx_cvr$n2i_con, dat_bg_glx_cvr$m1i, dat_bg_glx_cvr$sd1i, dat_bg_glx_cvr$n1i)
  
dat_bg_glx_cvr$cvr_VAR <- dat_bg_glx_VARcvr

dat_bg_glx_cvr$totn <- dat_bg_glx_cvr$n1i + dat_bg_glx_cvr$n2i_con

# does hedges g (SMD) differ between med and non-med
result4 <- rma(yi, vi, data=dat_bg_glx_cvr, method="REML", control=list(maxiter=1000, stepadj=0.5), mods=naive1)
result4 # NS

# does cvr differ between med and non-med
result5 <- rma(cvr, cvr_VAR, data=dat_bg_glx_cvr, method="REML", control=list(maxiter=1000, stepadj=0.5), mods=naive1)
result5 # NS


```

```{r}
# MODERATE BY MED 
# THALAMUS glu 
dat_thal_glu_cvr <- filter(dat, region == "thal", metabolite == "glu" )

# calc cvr
    dat_thal_glu_cvr2 <- Calc.lnCVR(dat_thal_glu_cvr$m2i, dat_thal_glu_cvr$sd2i,  dat_thal_glu_cvr$n2i_con, dat_thal_glu_cvr$m1i, dat_thal_glu_cvr$sd1i, dat_thal_glu_cvr$n1i)
    
dat_thal_glu_cvr$cvr <- dat_thal_glu_cvr2

# calc cvr var    
  dat_thal_glu_VARcvr <- Calc.var.lnCVR(dat_thal_glu_cvr$m2i, dat_thal_glu_cvr$sd2i, dat_thal_glu_cvr$n2i_con, dat_thal_glu_cvr$m1i, dat_thal_glu_cvr$sd1i, dat_thal_glu_cvr$n1i)
  
dat_thal_glu_cvr$cvr_VAR <- dat_thal_glu_VARcvr

dat_thal_glu_cvr$totn <- dat_thal_glu_cvr$n1i + dat_thal_glu_cvr$n2i_con

# does cvr differ between med and non-med
result6 <- rma(cvr, cvr_VAR, data=dat_thal_glu_cvr, method="REML", control=list(maxiter=1000, stepadj=0.5), mods=naive1)
result6 # NS

        
```

```{r}
# MODERATE BY MED 
# MFC glu 

dat_pfc_glu_cvr <- filter(dat, region == "pfc", metabolite == "glu" )

# calc cvr
    dat_pfc_glu_cvr2 <- Calc.lnCVR(dat_pfc_glu_cvr$m2i, dat_pfc_glu_cvr$sd2i,  dat_pfc_glu_cvr$n2i_con, dat_pfc_glu_cvr$m1i, dat_pfc_glu_cvr$sd1i, dat_pfc_glu_cvr$n1i)
    
dat_pfc_glu_cvr$cvr <- dat_pfc_glu_cvr2

# calc cvr var    
  dat_pfc_glu_VARcvr <- Calc.var.lnCVR(dat_pfc_glu_cvr$m2i, dat_pfc_glu_cvr$sd2i, dat_pfc_glu_cvr$n2i_con, dat_pfc_glu_cvr$m1i, dat_pfc_glu_cvr$sd1i, dat_pfc_glu_cvr$n1i)
  
dat_pfc_glu_cvr$cvr_VAR <- dat_pfc_glu_VARcvr

dat_pfc_glu_cvr$totn <- dat_pfc_glu_cvr$n1i + dat_pfc_glu_cvr$n2i_con

# does hedges g (SMD) differ between med and non-med
result5 <- rma(yi, vi, data=dat_pfc_glu_cvr, method="REML", control=list(maxiter=1000, stepadj=0.5), mods=naive1)
result5 # NS

#  Does CVR differ between med and unmed
result6 <- rma(cvr, cvr_VAR, data=dat_pfc_glu_cvr, method="REML", control=list(maxiter=1000, stepadj=0.5), mods=naive1)
result6 # NS


```













# GRAPH OF META-REGRESSIONS
# CVR
# MTL GLU
```{r}
# step 1

# filter it : hip glu age
dat$totn <- dat$n1i + dat$n2i_con
dat_hip_glu_cvr <- filter(dat, region == "hip", metabolite == "glu" )


# calc cvr
dat_hip_glu_cvr2 <- Calc.lnCVR(dat_hip_glu_cvr$m2i, dat_hip_glu_cvr$sd2i,  dat_hip_glu_cvr$n2i_con, dat_hip_glu_cvr$m1i, dat_hip_glu_cvr$sd1i, dat_hip_glu_cvr$n1i)
    
dat_hip_glu_cvr$cvr <- dat_hip_glu_cvr2


# calc cvr var    
  dat_hip_glu_VARcvr <- Calc.var.lnCVR(dat_hip_glu_cvr$m2i, dat_hip_glu_cvr$sd2i, dat_hip_glu_cvr$n2i_con, dat_hip_glu_cvr$m1i, dat_hip_glu_cvr$sd1i, dat_hip_glu_cvr$n1i)
  
dat_hip_glu_cvr$cvr_VAR <- dat_hip_glu_VARcvr

dat_hip_glu_cvr$totn <- dat_hip_glu_cvr$n1i + dat_hip_glu_cvr$n2i_con


```

```{r}
# step 2 graph 
# hip glU age

png('C:/Users/Me/Analysis/R/variance/results/meta_regression/hip_glu_age_combined2.png')

class(dat_hip_glu_cvr$age_combined) # age_combined is character format, so geom_smooth wont work
dat_hip_glu_cvr$age_combined <- as.numeric(dat_hip_glu_cvr$age_combined)

ggplot(data=dat_hip_glu_cvr, mapping = aes(x = age_combined, y=cvr, size=totn)) +
  geom_point(colour="blue", alpha=0.3) +
  geom_smooth(aes(), colour='blue', method = lm,  size=0.5) +
  labs(
    x = "Age",
    y = "CVR: Temporal Lobe Glutamate"
  ) +
  theme_minimal() +
  theme(legend.position = "none")


dev.off()

```




# GRAPH: BG Glu
```{r}
# step 1
# filter it for the analysis you want:

dat$totn <- dat$n1i + dat$n2i_con


dat_bg_glu_cvr <- filter(dat, region == "bg", metabolite == "glu" )

# calc cvr
    dat_bg_glu_cvr2 <- Calc.lnCVR(dat_bg_glu_cvr$m2i, dat_bg_glu_cvr$sd2i,  dat_bg_glu_cvr$n2i_con, dat_bg_glu_cvr$m1i, dat_bg_glu_cvr$sd1i, dat_bg_glu_cvr$n1i)
    
dat_bg_glu_cvr$cvr <- dat_bg_glu_cvr2

# calc cvr var    
  dat_bg_glu_VARcvr <- Calc.var.lnCVR(dat_bg_glu_cvr$m2i, dat_bg_glu_cvr$sd2i, dat_bg_glu_cvr$n2i_con, dat_bg_glu_cvr$m1i, dat_bg_glu_cvr$sd1i, dat_bg_glu_cvr$n1i)
  
dat_bg_glu_cvr$cvr_VAR <- dat_bg_glu_VARcvr

dat_bg_glu_cvr$totn <- dat_bg_glu_cvr$n1i + dat_bg_glu_cvr$n2i_con


```

```{r}
# STEP 2
# bg glu age

png('C:/Users/Me/Analysis/R/variance/results/meta_regression/bg_glu_age_combined.png')

class(dat_bg_glu_cvr$age_combined) # age_combined is character format, so geom_smooth wont work
dat_bg_glu_cvr$age_combined <- as.numeric(dat_bg_glu_cvr$age_combined)

ggplot(data=dat_bg_glu_cvr, mapping = aes(x = age_combined, y=cvr, size=totn)) +
  geom_point(colour="blue", alpha=0.3) +
  geom_smooth(aes(), colour='blue', method = lm,  size=0.5) +
  labs(
    x = "Age",
    y = "CVR: Basal Ganglia Glutamate"
  ) +
  theme_minimal() +
  theme(legend.position = "none")


dev.off()

```

```{r}
# bg glu pub panss_tot

png('C:/Users/Me/Analysis/R/variance/results/meta_regression/bg_glu_panss_tot.png')

class(dat_bg_glu_cvr$panss_tot) # panss_tot is character format, so geom_smooth wont work
dat_bg_glu_cvr$panss_tot <- as.numeric(dat_bg_glu_cvr$panss_tot)

ggplot(data=dat_bg_glu_cvr, mapping = aes(x = panss_tot, y=cvr, size=totn)) +
  geom_point(colour="blue", alpha=0.3) +
  geom_smooth(aes(), colour='blue', method = lm,  size=0.5) +
  labs(
    x = "PANSS Total Score",
    y = "CVR: Basal Ganglia Glutamate"
  ) +
  theme_minimal() +
  theme(legend.position = "none")


dev.off()

```




# GRAPH: PFC
```{r}
# step 1
# pfc gln panss_tot
# filter it for the analysis you want:
dat_pfc_gln_cvr <- filter(dat, region == "pfc", metabolite == "gln" )

# calc cvr
    dat_pfc_gln_cvr2 <- Calc.lnCVR(dat_pfc_gln_cvr$m2i, dat_pfc_gln_cvr$sd2i,  dat_pfc_gln_cvr$n2i_con, dat_pfc_gln_cvr$m1i, dat_pfc_gln_cvr$sd1i, dat_pfc_gln_cvr$n1i)
    
dat_pfc_gln_cvr$cvr <- dat_pfc_gln_cvr2

# calc cvr var    
  dat_pfc_gln_VARcvr <- Calc.var.lnCVR(dat_pfc_gln_cvr$m2i, dat_pfc_gln_cvr$sd2i, dat_pfc_gln_cvr$n2i_con, dat_pfc_gln_cvr$m1i, dat_pfc_gln_cvr$sd1i, dat_pfc_gln_cvr$n1i)
  
dat_pfc_gln_cvr$cvr_VAR <- dat_pfc_gln_VARcvr

dat_pfc_gln_cvr$totn <- dat_pfc_gln_cvr$n1i + dat_pfc_gln_cvr$n2i_con


```

```{r}
# step 2
# pfc gln panss_tot

png('C:/Users/Me/Analysis/R/variance/results/meta_regression/pfc_gln_panss_tot2.png')

class(dat_pfc_gln_cvr$panss_tot) # panss_tot is character format, so geom_smooth wont work
dat_pfc_gln_cvr$panss_tot <- as.numeric(dat_pfc_gln_cvr$panss_tot)

ggplot(data=dat_pfc_gln_cvr, mapping = aes(x = panss_tot, y=cvr, size=totn)) +
  geom_point(colour="blue", alpha=0.3) +
  geom_smooth(aes(), colour='blue', method = lm,  size=0.5) +
  labs(
    x = "PANSS Total Score",
    y = "CVR: MFC Glutamine"
  ) +
  theme_minimal() +
  theme(legend.position = "none")


dev.off()

```





```{r}
# pfc glu age

# step 1
# filter it for the analysis you want + # make cvr sheet

dat$totn <- dat$n1i + dat$n2i_con


dat_pfc_glu_cvr <- filter(dat, region == "pfc", metabolite == "glu" )

# calc cvr
    dat_pfc_glu_cvr2 <- Calc.lnCVR(dat_pfc_glu_cvr$m2i, dat_pfc_glu_cvr$sd2i,  dat_pfc_glu_cvr$n2i_con, dat_pfc_glu_cvr$m1i, dat_pfc_glu_cvr$sd1i, dat_pfc_glu_cvr$n1i)
    
dat_pfc_glu_cvr$cvr <- dat_pfc_glu_cvr2

# calc cvr var    
  dat_pfc_glu_VARcvr <- Calc.var.lnCVR(dat_pfc_glu_cvr$m2i, dat_pfc_glu_cvr$sd2i, dat_pfc_glu_cvr$n2i_con, dat_pfc_glu_cvr$m1i, dat_pfc_glu_cvr$sd1i, dat_pfc_glu_cvr$n1i)
  
dat_pfc_glu_cvr$cvr_VAR <- dat_pfc_glu_VARcvr

dat_pfc_glu_cvr$totn <- dat_pfc_glu_cvr$n1i + dat_pfc_glu_cvr$n2i_con
```

```{r}
# step 2:
# pfc glu age 

png('C:/Users/Me/Analysis/R/variance/results/meta_regression/pfc_glu_age.png')

class(dat_pfc_glu_cvr $age_combined) # age_combined is character format, so geom_smooth wont work
dat_pfc_glu_cvr $age_combined <- as.numeric(dat_pfc_glu_cvr $age_combined)

ggplot(data=dat_pfc_glu_cvr, mapping = aes(x = age_combined, y=cvr, size=totn)) +
  geom_point(colour="blue", alpha=0.3) +
  geom_smooth(aes(), colour='blue', method = lm,  size=0.5) +
  labs(
    x = "Age",
    y = "CVR: MFC Glutamate"
  ) +
  theme_minimal() +
  theme(legend.position = "none")


dev.off()

```






# GRAPH: META-REGRESSION 
# for effect sizes (SMD)
# AGE
```{r}
# REGRESSION FOR EFFECT SIZES
# Effect size (yi)
# White matter glx & Age 

dat$totn <- dat$n1i + dat$n2i_con

dat_wm_pfc_glx <- filter(dat, region == "wm_pfc", metabolite == "glx" )

png('C:/Users/Me/Analysis/R/variance/results/meta_regression/smd/wm_pfc_glx_age_combined.png')

class(dat_wm_pfc_glx $age_combined) # age_combined is character format, so geom_smooth wont work
dat_wm_pfc_glx $age_combined <- as.numeric(dat_wm_pfc_glx $age_combined)

ggplot(data=dat_wm_pfc_glx , mapping = aes(x = age_combined, y=yi, size=totn)) +
  geom_point(colour="darkgreen", alpha=0.3) +
  geom_smooth(aes(), colour='darkgreen', method = lm,  size=0.5) +
  geom_hline(yintercept = 0, linetype=3) +
  labs(
    x = "Age",
    y = "Effect size: Frontal White Matter Glx"
  ) +
  theme_minimal() +
  theme(legend.position = "none")

dev.off()
```

```{r}
# REGRESSION FOR EFFECT SIZES
# effect size (yi)
# White matter glu & Age

dat$totn <- dat$n1i + dat$n2i_con

dat_wm_pfc_glu <- filter(dat, region == "wm_pfc", metabolite == "glu" )

png('C:/Users/Me/Analysis/R/variance/results/meta_regression/smd/wm_pfc_glu_age_combined.png')

class(dat_wm_pfc_glu $age_combined) # age_combined is character format, so geom_smooth wont work
dat_wm_pfc_glu $age_combined <- as.numeric(dat_wm_pfc_glu $age_combined)

ggplot(data=dat_wm_pfc_glu , mapping = aes(x = age_combined, y=yi, size=totn)) +
  geom_point(colour="darkgreen", alpha=0.3) +
  geom_smooth(aes(), colour='darkgreen', method = lm,  size=0.5) +
  geom_hline(yintercept = 0, linetype=3) +
  labs(
    x = "Age",
    y = "Effect size: Frontal White Matter Glutamate"
  ) +
  theme_minimal() +
  theme(legend.position = "none")

dev.off()
```

```{r}
# REGRESSION FOR EFFECT SIZES
# effect size (yi)
# BG gln + Age

dat$totn <- dat$n1i + dat$n2i_con

dat_bg_gln <- filter(dat, region == "bg", metabolite == "gln" )

png('C:/Users/Me/Analysis/R/variance/results/meta_regression/smd/bg_gln_age_combined.png')

class(dat_bg_gln $age_combined) # age_combined is character format, so geom_smooth wont work
dat_bg_gln $age_combined <- as.numeric(dat_bg_gln $age_combined)

ggplot(data=dat_bg_gln , mapping = aes(x = age_combined, y=yi, size=totn)) +
  geom_point(colour="darkgreen", alpha=0.3) +
  geom_smooth(aes(), colour='darkgreen', method = lm,  size=0.5) +
  geom_hline(yintercept = 0, linetype=3) +
  labs(
    x = "Age",
    y = "Effect size: Basal Ganglia Glutamine"
  ) +
  theme_minimal() +
  theme(legend.position = "none")

dev.off()
```








# META-REGRESSION GRAPHS: SMD + MALE %
```{r}
# REGRESSION FOR EFFECT SIZES
# effect size (yi)
# white matter glx + male

dat$totn <- dat$n1i + dat$n2i_con

dat_wm_pfc_glx <- filter(dat, region == "wm_pfc", metabolite == "glx" )

png('C:/Users/Me/Analysis/R/variance/results/meta_regression/smd/wm_pfc_glx_male_combined.png')

class(dat_wm_pfc_glx $male_combined) # male_combined is character format, so geom_smooth wont work
dat_wm_pfc_glx $male_combined <- as.numeric(dat_wm_pfc_glx $male_combined)

ggplot(data=dat_wm_pfc_glx , mapping = aes(x = male_combined, y=yi, size=totn)) +
  geom_point(colour="darkgreen", alpha=0.3) +
  geom_smooth(aes(), colour='darkgreen', method = lm,  size=0.5) +
  geom_hline(yintercept = 0, linetype=3) +
  labs(
    x = "Proportion of Males %",
    y = "Effect size: Frontal White Matter Glx"
  ) +
  theme_minimal() +
  theme(legend.position = "none")

dev.off()
```

```{r}
# REGRESSION FOR EFFECT SIZES
# effect size (yi)
# mfc glu + Male %
dat$totn <- dat$n1i + dat$n2i_con

dat_pfc_glu <- filter(dat, region == "pfc", metabolite == "glu" )

png('C:/Users/Me/Analysis/R/variance/results/meta_regression/smd/pfc_glu_male_combined.png')

class(dat_pfc_glu $male_combined) # age_combined is character format, so geom_smooth wont work
dat_pfc_glu $male_combined <- as.numeric(dat_pfc_glu $male_combined)

ggplot(data=dat_pfc_glu , mapping = aes(x = male_combined, y=yi, size=totn)) +
  geom_point(colour="darkgreen", alpha=0.3) +
  geom_smooth(aes(), colour='darkgreen', method = lm,  size=0.5) +
  geom_hline(yintercept = 0, linetype=3) +
  labs(
    x = "Proportion of Males %",
    y = "Effect size: MFC Glutamate"
  ) +
  theme_minimal() +
  theme(legend.position = "none")

  
dev.off()

```








# META-REGRESSION GRAPH: SMD + PANSS
```{r}
# REGRESSION FOR EFFECT SIZES
# effect size (yi)
#  panss_tot bg glu
dat$totn <- dat$n1i + dat$n2i_con

dat_bg_glu <- filter(dat, region == "bg", metabolite == "glu" )

class(dat_bg_glu $panss_tot) # panss_tot is character format, so geom_smooth wont work
dat_bg_glu $panss_tot <- as.numeric(dat_bg_glu $panss_tot)

png('C:/Users/Me/Analysis/R/variance/results/meta_regression/smd/bg_glu_panss_tot.png')



ggplot(data=dat_bg_glu , mapping = aes(x = panss_tot, y=yi, size=totn)) +
  geom_point(colour="darkgreen", alpha=0.3) +
  geom_smooth(aes(), colour='darkgreen', method = lm,  size=0.5) +
  geom_hline(yintercept = 0, linetype=3) +
  labs(
    x = "PANSS Total Score",
    y = "Effect size: Basal Ganglia Glutamate"
  ) +
  theme_minimal() +
  theme(legend.position = "none")

dev.off()
```

```{r}
# REGRESSION FOR EFFECT SIZES
# effect size (yi)
#  panss_tot dlpfc glu
dat$totn <- dat$n1i + dat$n2i_con

dat_dlpfc_glu <- filter(dat, region == "dlpfc", metabolite == "glu" )

class(dat_dlpfc_glu $panss_tot) # panss_tot is character format, so geom_smooth wont work
dat_dlpfc_glu $panss_tot <- as.numeric(dat_dlpfc_glu $panss_tot)

png('C:/Users/Me/Analysis/R/variance/results/meta_regression/smd/dlpfc_glu_panss_tot.png')



ggplot(data=dat_dlpfc_glu , mapping = aes(x = panss_tot, y=yi, size=totn)) +
  geom_point(colour="darkgreen", alpha=0.3) +
  geom_smooth(aes(), colour='darkgreen', method = lm,  size=0.5) +
  geom_hline(yintercept = 0, linetype=3) +
  labs(
    x = "PANSS Total Score",
    y = "Effect size: DLPFC Glutamate"
  ) +
  theme_minimal() +
  theme(legend.position = "none")

dev.off()
```

```{r}
# REGRESSION FOR EFFECT SIZES
# effect size (yi)
#  panss_tot hip glu
dat$totn <- dat$n1i + dat$n2i_con

dat_hip_glu <- filter(dat, region == "hip", metabolite == "glu" )

png('C:/Users/Me/Analysis/R/variance/results/meta_regression/smd/hip_glu_panss_tot.png')

class(dat_hip_glu $panss_tot) # panss_tot is character format, so geom_smooth wont work
dat_hip_glu $panss_tot <- as.numeric(dat_hip_glu $panss_tot)

ggplot(data=dat_hip_glu , mapping = aes(x = panss_tot, y=yi, size=totn)) +
  geom_point(colour="darkgreen", alpha=0.3) +
  geom_smooth(aes(), colour='darkgreen', method = lm,  size=0.5) +
  geom_hline(yintercept = 0, linetype=3) +
  labs(
    x = "PANSS Total Score",
    y = "Effect size: Temporal Lobe Glutamate"
  ) +
  theme_minimal() +
  theme(legend.position = "none")

dev.off()
```








# META-REGRESSION GRAPH: SMD + CPZ
```{r}
# REGRESSION FOR EFFECT SIZES
# effect size (yi)
#  cpz hip glu
dat$totn <- dat$n1i + dat$n2i_con

dat_hip_glx <- filter(dat, region == "hip", metabolite == "glx" )

png('C:/Users/Me/Analysis/R/variance/results/meta_regression/smd/hip_glx_cpz.png')

class(dat_hip_glx $cpz) # cpz is character format, so geom_smooth wont work
dat_hip_glx $cpz <- as.numeric(dat_hip_glx $cpz)

ggplot(data=dat_hip_glx , mapping = aes(x = cpz, y=yi, size=totn)) +
  geom_point(colour="darkgreen", alpha=0.3) +
  geom_smooth(aes(), colour='darkgreen', method = lm,  size=0.5) +
  geom_hline(yintercept = 0, linetype=3) +
  labs(
    x = "Chlorpromazine Dose Equivalent",
    y = "Effect size: Temporal Lobe Glx"
  ) +
  theme_minimal() +
  theme(legend.position = "none")

dev.off()
```



